Model LF

### 2022-10-30 max_dp endogen stød.Rmd
Commit

nl_g_bs4 = Shock_bs4$simulation$nl_g

yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
```

@@

yk_ds_04 = Shock_4$simulation$yk_ds
emp_04 = Shock_4$simulation$emp
wage_ds_04 = Shock_4$simulation$wage_ds
ur_ds_04 = Shock_4$simulation$ur_ds
pc_ds_04 = Shock_4$simulation$pc_ds
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
pconk_ds_04 = Shock_4$simulation$pconk_ds
komp_r_04 = Shock_4$simulation$komp_r
max_dp_04 = Shock_4$simulation$max_dp
nben_h_04 = Shock_4$simulation$nben_h
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
ik_04 = Shock_4$simulation$ik
wage_ds_t_04 = Shock_4$simulation$wage_ds_t
nben_h_un_04 = Shock_4$simulation$nben_h_un
nl_g_04 = Shock_4$simulation$nl_g
nsben_h_04 = Shock_4$simulation$nsben_h
dp_person_04 = Shock_4$simulation$dp_person
part1_04 = Shock_4$simulation$part1
u_ds_04 = Shock_4$simulation$u_ds
kont_h_ratio_04 = Shock_4$simulation$kont_h_ratio
part_04 = Shock_4$simulation$part

rw_ds_04 = Shock_4$simulation$rw_ds
kuld_04 = Shock_4$simulation$shock_kuld
```

@@

```{r}
plot((emp_04-emp_bs4)*1000, col= "red")
```

@@

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-350, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((nl_g_07 - nl_g_bs7)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending");
lines(((nl_g_04 - nl_g_bs4)), col= "black");
lines(((nl_g_02 - nl_g_bs2)), col= "red");
lines(((nl_g_01 - nl_g_00)), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.0001, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_07 - yk_ds_bs7) / yk_ds_bs7), col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","All channels but productivity","Insurance rate channel", "Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "yellow","red", "black","orange", "green"));
grid()
```

>>>>

nl_g_bs4 = Shock_bs4$simulation$nl_g
unemp_bs4 = Shock_bs4$simulation$unemp
yd_hk_ds_bs4 = Shock_bs4$simulation$yd_hk_ds
wage_gap1_bs4 = Shock_bs4$simulation$wage_gap1
wage_gap_bs4 = Shock_bs4$simulation$wage_gap
prod_bs4 = Shock_bs4$simulation$prod
```

@@

yk_ds_04 = Shock_4$simulation$yk_ds
emp_04 = Shock_4$simulation$emp
wage_ds_04 = Shock_4$simulation$wage_ds
ur_ds_04 = Shock_4$simulation$ur_ds
pc_ds_04 = Shock_4$simulation$pc_ds
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
pconk_ds_04 = Shock_4$simulation$pconk_ds
komp_r_04 = Shock_4$simulation$komp_r
max_dp_04 = Shock_4$simulation$max_dp
nben_h_04 = Shock_4$simulation$nben_h
yd_hk_ds_04 = Shock_4$simulation$yd_hk_ds
ik_04 = Shock_4$simulation$ik
wage_ds_t_04 = Shock_4$simulation$wage_ds_t
nben_h_un_04 = Shock_4$simulation$nben_h_un
nl_g_04 = Shock_4$simulation$nl_g
nsben_h_04 = Shock_4$simulation$nsben_h
dp_person_04 = Shock_4$simulation$dp_person
part1_04 = Shock_4$simulation$part1
u_ds_04 = Shock_4$simulation$u_ds
kont_h_ratio_04 = Shock_4$simulation$kont_h_ratio
part_04 = Shock_4$simulation$part
unemp_04 = Shock_4$simulation$unemp
rw_ds_04 = Shock_4$simulation$rw_ds
kuld_04 = Shock_4$simulation$shock_kuld
```

@@

```{r}
plot((unemp_04-unemp_bs4)*1000, col= "red")
```

@@

```{r}
plot(((emp_07 - emp_bs7)*1000), col= "blue", xlab= "Year", ylab= "Change in employment (people)", main= "Change in Employment", ylim= c(-1500, 300));
lines(((emp_04 - emp_bs4)*1000), col= "black");
lines(((emp_02 - emp_bs2)*1000), col= "red");
lines(((emp_01 - emp_00)*1000), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
((emp_07 - emp_bs7)*1000)
```

```{r}
plot(((nl_g_07 - nl_g_bs7)), col= "blue", xlab= "Year", ylab= "Change in Government net lending", main= "Change in Government net-lending", ylim= c(-200, 500));
lines(((nl_g_04 - nl_g_bs4)), col= "black");
lines(((nl_g_02 - nl_g_bs2)), col= "red");
lines(((nl_g_01 - nl_g_00)), col= "green");
legend("left", legend=c("All channels except productivity", "insurance rate channel", "wage channel", "demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue","black","red", "green"));
grid()
```

```{r}
plot(((yk_ds_05 - yk_ds_bs56) / yk_ds_bs56), col= "blue", xlab= "Year", ylab= "% Change in Gdp", main= "Gdp", ylim= c(-0.001, 0.0015));
lines(((yk_ds_04 - yk_ds_bs4) / yk_ds_bs4), col= "yellow");
lines(((yk_ds_07 - yk_ds_bs7) / yk_ds_bs7), col= "red");
lines(((yk_ds_03 - yk_ds_bs3) / yk_ds_bs3), col= "black");
lines(((yk_ds_02 - yk_ds_bs2) / yk_ds_bs2), col= "orange");
lines(((yk_ds_01 - yk_ds_00) / yk_ds_00), col= "green");
legend("left", legend=c("All channels","Insurance rate channel", "All channels but productivity","Productivity channel", "Wage channel", "Demand channel"),
       lty=c(1),lwd=c(2),bty="n", col = c("blue", "yellow","red", "black","orange", "green"));
grid()
```
